---
title: "Discrete Probability"
author: "Dr. Qiusheng Wu"
output: 
  html_notebook:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Counting the number of combinations
Calculate the number of combinations of n items taken k at a time

```{r}
choose(3,2)
factorial(3)/(factorial(2)*factorial(3-2))
```


## Generating combinations
Generate all combinations of n items taken k at a time

```{r}
combn(1:5,3)
combn(c("T1","T2","T3","T4","T5"),3)
```

## Generating random numbers
Generates one uniform random number
```{r}
runif(1)
runif(10)
runif(10,min = -3,max = 3)
```
```{r}
hist(runif(1000))
```

Generates one random value from the standard normal distribution
```{r}
rnorm(10)
rnorm(10,mean = 100,sd = 15)
rnorm(3,mean = c(-10,0,10),sd = 1)
```

```{r}
hist(rnorm(1000))
```


## Generating reproducible random numbers
generate a sequence of random numbers, but you want to reproduce the same sequence every time your program runs
```{r}
set.seed(100)
runif(10)
set.seed(100)
runif(10)
```

## Generating a random sample
```{r}
library(MASS)
df <- Cars93
sample(df$Price, 10)
sample(df$Manufacturer,10)
```

## Generating random sequences
```{r}
set.seed(100)
sample(1:10)
sample(1:10,size = 10,replace = FALSE)
sample(c("H","T"),size = 10,replace = TRUE)
sample(c("blue","yellow","red","green","purple"),size = 5,replace = FALSE)
```

```{r}
births <- sample(c("boy","girl"),size = 10,replace = TRUE,prob = c(0.513,0.487))
births
table(births)
manybirths <- sample(c("boy","girl"),size = 100000,replace = TRUE,prob = c(0.513,0.487))
table(manybirths)
```

## Binomial Distribution
### Probability functions
Density function: `dbinom(x, size, prob)` <br>
Cumulative probability function: `pbinom(q, size, prob, lower.tail = TRUE)`


```{r}
dbinom(5,size = 10,prob = 0.5)
dbinom(7,size = 10,prob = 0.5)
pbinom(7,size = 10,prob = 0.5)
pbinom(7,size = 10,prob = 0.5,lower.tail = FALSE)

dbinom(6,size = 10,prob = 0.5) + dbinom(7,size = 10,prob = 0.5)
pbinom(7,size = 10,prob = 0.5) - pbinom(5,size = 10,prob = 0.5)
pbinom(c(5,7),size = 10,prob = 0.5)
diff(pbinom(c(5,7),size = 10,prob = 0.5))
```

### Plot probability functions
```{r}
n <- 20
x <- 0:n
y <- dbinom(x,size = n,prob = 0.5)
plot(x,y)
plot(x,y,type = "b",pch = 16,col="black")


n <- 20
x <- 0:n
y <- pbinom(x,size = n,prob = 0.5)
plot(x,y)
plot(x,y,type = "b",pch = 16,col="black")


x <- seq(from = -3,to = 3,length.out = 100)
y <- dnorm(x)
plot(x,y)
plot(x,y,type = "l",pch = 16,col="black")
```

## Geometric distribution
If the probability of success on each trial is p, then the probability that the kth trial (out of k trials) is the first success is:
x represents the number of failures in a sequence of Bernoulli trials before success occurs.

`dgeom(x, prob)` <br>
`pgeom(x, prob)`


```{r}
dgeom(0,prob = 0.5)
dgeom(1,prob = 0.5)

n <- 10
x <- 0:n
y <- dgeom(x,prob = 0.5)
plot(x,y)
plot(x,y,type = "b",pch = 16,col="black",ylim = c(0,1))

y2 <- dgeom(x, prob=0.8)
lines(x,y2,type = "b",pch = 16,col="red")

y3 <- dgeom(x, prob=0.2)
lines(x,y3,type = "b",pch = 16,col="blue")

```

## Poisson Distribution
During the last 60 days, there were 3 accidents. What’s the probability that there will be more than 3 accidents during the next month?<br>
`dpois(x, lambda)` <br>
`ppois(q, lambda, lower.tail = TRUE)`

```{r}
dpois(0,lambda = 1.5)
dpois(1,lambda = 1.5)
dpois(2,lambda = 1.5)
dpois(3,lambda = 1.5)
1- dpois(0,1.5)-dpois(1,1.5)-dpois(2,1.5)-dpois(3,1.5)

ppois(3,lambda = 1.5,lower.tail = FALSE)
```

```{r}
n <- 20
x <- 0:n
y <- dpois(x,lambda = 1)
plot(x,y)
plot(x,y,type = "b",pch = 16,col="black")

y2 <- dpois(x,lambda = 4)
lines(x,y2,type = "b",pch = 16,col="red")

y3 <- dpois(x,lambda = 10)
lines(x,y3,type = "b",pch = 16,col="blue")
```


