---
title: "GEOG-533 Lab 3"
author: "Firstname Lastname"
output:
  html_notebook:
    toc: yes
    toc_float: yes
---

## Question 1
The number of points scored by each team in a tournament is normally distributed, with mean μ = 32 and standard deviation σ = 7. What is the probability of:

### Question 1.1
A team scoring 20 points or fewer? Plot the density function and shade the area. (5 pt.)

```{r}

```

### Question 1.2
A team scoring more than 35 points? Plot the density function and shade the area. (5 pt.)
```{r}

```


### Question 1.3
A team scoring between 20 and 40 points? Plot the density function and shade the area. (5 pt.)
```{r}

```


## Question 2
The number of comments per post on a social media site is exponentially distributed, with the average post receiving ten comments. What percentage of posts get: 

### Question 2.1
Fewer than three comments?  Plot the density function and shade the area. (5 pt.)
```{r}

```

### Question 2.2
More than 20 comments? Plot the density function and shade the area. (5 pt.)
```{r}

```


### Question 2.3
Between five and ten comments? Plot the density function and shade the area. (5 pt.)
```{r}

```


## Question 3
Basic raster creation and calculation:

### Question 3.1
Create a first raster (30 rows × 30 columns) and assign values to the raster based on random values from a uniform distribution. Plot the raster and the histogram. (5 pt.)
```{r}

```

### Question 3.2
Create a second raster (30 rows × 30 columns) and assign values to the raster based on random values from a normal distribution. Plot the raster and the histogram. (5 pt.)
```{r}

```


### Question 3.3
Create a third raster (30 rows × 30 columns) and assign values to the raster based on cell-by-cell addition of the first raster and the second raster.  Plot the raster and the histogram. (5 pt.)
```{r}

```


### Question 3.4
Calculate the mean value of the third raster. Reclassify the third raster into a binary image: 1 (cell value > mean value) and 0 (cell value <= mean value).  Save the reclassified image to your working directory as a TIFF image. (5 pt.)
```{r}

```

