---
title: "Continuous Probability"
author: "Dr. Qiusheng Wu"
output: 
  html_notebook:
    toc: True
    toc_float: TRUE
---

## Uniform Distribution
A uniform distribution, sometimes also known as a rectangular distribution, is a distribution that has constant probability.

### Generating Random Samples
function: `runif(n, min = 0, max = 1)`
```{r}
runif(10)  ## Generating 10 random numbers following uniform distribution
x <- runif(100)
hist(x)
x <- runif(10000)  ## ## Generating 10,000 random numbers following uniform distribution
hist(x)
x <- runif(1000000) ## Generating 1,000,000 random numbers following uniform distribution
hist(x)
```

### Probability Density Function
function: `dunif(x, min = 0, max = 1)`
```{r}
x <- runif(100,min = 0,max = 300)
y <- dunif(x,min = 100,max = 200)
plot(x,y)
```

### Cumulative Distribution Function
function: `punif(q, min = 0, max = 1, lower.tail = TRUE)`
```{r}
x <- runif(100,min = 0,max = 300)
y2 <- punif(x,min = 100,max = 200)
plot(x,y2,xlim = c(0,300))
```

### Ploting using the `curve` function
```{r}
curve(dunif(x,min = 100,max = 200),from = 0,to = 300,n = 1000)
curve(punif(x,min = 100,max = 200),from = 0,to = 300,n = 1000)
curve(sin(x), -2*pi, 2*pi, xname = "x",n = 1000)
curve(cos(x2), -2*pi, 2*pi, xname = "x2",n = 1000)
```

## Normal Distribution
### Generating Random Samples
function: `rnorm(n, mean = 0, sd = 1)`
```{r}
rnorm(10)  ## Generating 10 random numbers following normal distribution
x <- rnorm(100)
hist(x)
x <- rnorm(10000)  ## ## Generating 10,000 random numbers following normal distribution
hist(x)
x <- rnorm(1000000) ## Generating 1,000,000 random numbers following normal distribution
hist(x)
```

### Probability Density Function
function: `dnorm(x, mean = 0, sd = 1)`
```{r}
x <- seq(-5,5,by = 0.01)
y1 <- dnorm(x)
plot(x, y1, type = "l", xlim = c(-5,5), ylim = c(0,1), lwd = 2, col = "red")
y2 <- dnorm(x,-2,sqrt(0.5))
lines(x, y2, type = "l", xlim = c(-5,5), ylim = c(0,1), lwd = 2, col = "green")
y3 <- dnorm(x,0,sqrt(0.2))
lines(x, y3, type = "l", xlim = c(-5,5), ylim = c(0,1), lwd=2, col="blue")
```

```{r}
curve(dnorm(x,0,1),from = -6,to = 6,col="red",lwd=2,xlim=c(-5,5),ylim=c(0,1))
curve(dnorm(x,-2,sqrt(0.5)),from = -6,to = 6,col="green",lwd=2,xlim=c(-5,5),ylim=c(0,1),add = TRUE)
curve(dnorm(x,0,sqrt(0.2)),from = -6,to = 6,col="blue",lwd=2,xlim=c(-5,5),ylim=c(0,1),add = TRUE,n = 500)
legend('topright',legend = c("N(0,1)","N(-2,0.5)","N(0,0.2)"), lty=1, lwd=2,col=c('red', 'green', 'blue'), bty='n', cex=1)

```
### Shading a Region of Interest
```{r}
curve(dnorm(x,0,1),xlim=c(-3,3),main='Normal Density')
cord.x <- c(-2,seq(-2,2,0.01),2) 
cord.y <- c(0,dnorm(seq(-2,2,0.01)),0) 
curve(dnorm(x,0,1),xlim=c(-3,3),main='Standard Normal',lwd=2) 
polygon(cord.x,cord.y,col='red')
polygon(cord.x,cord.y,density = 10)
```

## Exponential Distribution

Genrate random numbers following exponential function: `rexp(n, rate = 1)` <br>


```{r}
x <- rexp(1000,rate = 0.5)
hist(x,xlim = c(0,10))
```

```{r}
x <- rexp(1000,rate = 1)
hist(x,xlim = c(0,10))
```

```{r}
x <- rexp(1000,rate = 3)
hist(x,xlim = c(0,10))
```

density function: `dexp(x, rate = 1)` <br>
cumulative distribution function: `pexp(q, rate = 1, lower.tail = TRUE)`

```{r}
curve(dexp(x,1),xlim = c(0,5),ylim=c(0,1.6),lwd=2,col="red")
curve(dexp(x,0.5),xlim = c(0,5),lwd=2,col="green",add=TRUE)
curve(dexp(x,1.5),xlim = c(0,5),lwd=2,col="blue",add=TRUE)
legend('topright',legend = c("rate = 1","rate = 0.5","rate = 1.5"), lty=1, lwd=2,col=c('red', 'green', 'blue'), bty='n', cex=1)

```

## Raster function

Install rgdal and raster packages
```{r message=FALSE, warning=FALSE}
if(!require(rgdal)) install.packages("rgdal")
if(!require(raster)) install.packages("raster")
```


```{r}
library(raster)
ras <- raster(nrows=10,ncols=10,xmn=0,xmx=10,ymn=0,ymx=10)
ras
ras[] <- runif(ncell(ras))
plot(ras)
hist(ras)
cellStats(ras,"mean")
ras[1,1] <- 0
ras[ras > 0.5] <- 1
ras2 <- ras + ras * 10
plot(ras2)
writeRaster(ras2,filename = "test.tif",overwrite=TRUE)

```

