---
title: "Inferential Statistics"
author: "Dr. Qiusheng Wu"
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
---

## Generating random samples

Suppose that we interview 500 students on campus, and the results show that the average student spends about 100 minutes each day preparing for classes with a standard deviation of 10 minutes. 

```{r}
n <- 500
time.mean <- 100
time.sd <- 10
student <- rnorm(n,mean = time.mean,sd=time.sd)
hist(student,breaks = 10,xlab="Time spent daily (minutes)")
print(mean(student))
print(sd(student))
```

## Sampling distribution of the mean
What if we repeat the interview many times, e.g., 300 times?
```{r}
n <- 5000
m <- 300
time.mean <- 100
time.sd <- 10
v <- vector()
for (i in 1:m) {
  x <- rnorm(n,time.mean,time.sd)
  avg <- mean(x)
  std <- sd(x)
  v <- c(v,avg)
  # print(avg)
  # print(std/sqrt(n))
}
hist(v,breaks = 15,freq = FALSE,xlab = "Sample mean (minutes)")
curve(dnorm(x,mean(v),sd(v)),from = 95,to = 105,add = TRUE,n = 400,col = "red")
mean(v)
sd(v)
```

## Confidence interval for the mean
```{r}
q90 <- qnorm(0.95)  # 90% confidence interval
curve(dnorm,from = -3,to = 3,main = "90% confidence interval")
x <- c(-q90,seq(-q90,q90,by = 0.01),q90)
y <- c(0,dnorm(seq(-q90,q90,by = 0.01)),0)
polygon(x,y,col = "red")
```

qnorm(0.95) = `r round(q90,2)`

```{r}
q95 <- qnorm(0.975)  # 95% confidence interval
curve(dnorm,from = -3,to = 3,main="95% confidence interval")
x <- c(-q95,seq(-q95,q95,by = 0.01),q95)
y <- c(0,dnorm(seq(-q95,q95,by = 0.01)),0)
polygon(x,y,col="green")
```

qnorm(0.975) = `r round(q95,2)`

```{r}
q99 <- qnorm(0.995) # 99% confidence interval
curve(dnorm,from = -3,to = 3,main="99% confidence interval")
x <- c(-q99,seq(-q99,q99,by = 0.01),q99)
y <- c(0,dnorm(seq(-q99,q99,by = 0.01)),0)
polygon(x,y,col="blue")
```

qnorm(0.995) = `r round(q99,2)`

Suppose that we interview 500 students on campus, and the results show that the average student spends about 100 minutes each day preparing for classes with a standard deviation of 10 minutes. Find 90%, 95%, and 99% confidence intervals.
```{r}
q90 <- qnorm(0.950)  # 90% confidence interval
round(q90,2)
q95 <- qnorm(0.975)  # 95% confidence interval
round(q95,2)
q99 <- qnorm(0.995)  # 99% confidence interval
round(q99,2)
std.err <- 10/sqrt(500)
conf.90 <- c(100-q90*std.err,100+q90*std.err) #[99.26, 100.74]
round(conf.90,2)
conf.95 <- c(100-q95*std.err,100+q95*std.err) #[99.12, 100.88]
round(conf.95,2)
conf.99 <- c(100-q99*std.err,100+q99*std.err) #[98.85, 101.15]
round(conf.99,2)
```

## Using mvrnorm function
How to generate random samples from the specified normal distribution with the exact mean and standard deviation?

```{r}
library(MASS)
x <- mvrnorm(n = 500,mu = 100,Sigma = 100,empirical = TRUE)
mean(x)
sd(x)
```

## Finding Confidence Interval 

### Problem
You have a sample from a population. Given that sample, you want to determine a confidence interval for the population’s mean.

### Solution
* Apply the t.test function to your sample `x`:
* `t.test(x)`
* The output includes a confidence interval at the 95% confidence level. To see intervals at other levels, use the conf.level argument.

### Example
```{r}
library(MASS)
x <- mvrnorm(n = 500,mu = 100,Sigma = 100,empirical = TRUE)
t.test(x,conf.level = 0.90)    #[99.26, 100.74]
t.test(x,conf.level = 0.95)    #[99.12, 100.88]
t.test(x,conf.level = 0.99)    #[98.84, 101.16]

```

### How to extract confidence interval out of t.test() output?

```{r}
library(MASS)
x <- mvrnorm(n = 500,mu = 100,Sigma = 100,empirical = TRUE)
result <- t.test(x,conf.level = 0.95)  
print(result)
conf.int <- result$conf.int
print(conf.int)
conf.level <- attr(result$conf.int, "conf.level")
print(conf.level)
```


## One-sample t-test

### Problem
Suppose that we interview 50 students on campus, and the results show that the average student spends about 99 minutes each day preparing for classes with a standard deviation of 10 minutes. 

***Null hypothesis***

$H_o:\mu = 100$

***Alternative hypothesis***

$H_{\alpha}:\mu \neq 100$

### Example
```{r}
library(MASS)
x <- mvrnorm(n = 500,mu = 99,Sigma = 100,empirical = TRUE)
result <- t.test(x,mu = 100)
result
if(result$p.value>0.05){
  print("We cannot reject the null hypothesis")
} else {
  print("We reject the null hypothesis")}
```

## Two-sample t-test

### Problem

Suppose that we interview **50 students** on campus, and the results show that the average student spends about **99 minutes** each day preparing for classes with a standard deviation of **10 minutes**. 

Suppose that we interview another **50 students** on campus, and the results show that the average student spends about **98 minutes** each day preparing for classes with a standard deviation of **5 minutes**. 

***Null hypothesis***

$H_o: \mu_1 = \mu_2$

***Alternative hypothesis***

$H_o: \mu_1 \neq \mu_2$

### Example
```{r}
library(MASS)
x1 <- mvrnorm(n = 50,mu = 99,Sigma = 100,empirical = TRUE)
x2 <- mvrnorm(n = 50,mu = 98,Sigma = 25,empirical = TRUE)
result <- t.test(x1,x2)
result
if(result$p.value>0.05){
  print("We cannot reject the null hypothesis")
} else {
  print("We reject the null hypothesis")}
```

## Student's t distribution
### Solution
* `dt(x, df)`
* `pt(q, df,lower.tail = TRUE)`
* `qt(p, df,lower.tail = TRUE)`
* `rt(n, df)`

### Example
```{r}
qnorm(0.95)
qnorm(0.975)
qnorm(0.995)
qt(0.95,df = 10)
qt(0.975,df = 10)
qt(0.995,df = 10)
curve(dt(x,df = 1),from = -5,to = 5,ylim = c(0,0.4),col = "red")
curve(dt(x,df = 2),from = -5,to = 5,col = "green",add=TRUE)
curve(dt(x,df = 5),from = -5,to = 5,col = "blue",add = TRUE)
curve(dnorm,add=TRUE,col ="black",lwd=2)

```

## Testing a sample proportion

### Problem
We want to test the hypothesis that more than 30% of U.S. households have internet access (with a significance level of 5%). We collect a sample of 150 households and find that 57 have access.

### Solution
```{r}
result <- prop.test(57,n = 150,p = 0.3,alternative = "greater")
result
if(result$p.value>0.05) {
  print("We cannot reject the null hypothesis ")
} else {
  print("We accept the alternative hypothesis")
}

```

## Two-sample proportion test
### Problem
A random sample of 428 adults from New York City reveals 128 smokers. A random sample of 682 adults from San Francisco reveals 170 smokers. Is the proportion of adult smokers in New York City different from that in San Francisco? 

### Solution
```{r}
result <- prop.test(x=c(128,170), n=c(428,682))
result
if(result$p.value>0.05) {
  print("We cannot reject the null hypothesis ")
} else {
  print("We accept the alternative hypothesis")
}
```


## Online equation editor
* <https://www.codecogs.com/latex/eqneditor.php>
* <http://rogercortesi.com/eqn/>
