---
title: "GEOG-533 Lab 1"
author: Firstname Lastname
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_notebook
---

## Instruction for lab submission

1. Make sure you change the **author** field above to your own *Firstname Lastname*
2. Create a zip file named **Firstname_Lastname_Lab_01.zip**, which contains **Lab_01.Rmd** and **Lab_01.nb.html**
3. Submit **Firstname_Lastname_Lab_01.zip** to [myCourses](https://mycourses.binghamton.edu) 

## Questions

**Cars93** in the **MASS** package contains data from 93 cars on sale in the USA in 1993.

Load the library and the dataset.
```{r}
library(MASS)
df <- Cars93
?Cars93
```

Check the metadata and compute the summary statistics.
```{r}
str(df)
summary(df)
```


### Question 1

The **Type** variable classifies the type of market the car is aimed at. Find the cheapest (**Price**) car in each type, and the car with the greatest fuel efficiency (**MPG.highway**). Find out the **Manufacturer** and Model. (20 pt.)

```{r}

```


### Question 2

Compute the mean **Horsepower** for each type, and the difference between each cars horsepower and the mean for its type. Based on the difference values, calculate the skewness and kurtosis (10 pt.)

```{r}

```


### Question 3

Create two new data frames for USA and non-USA cars. (10 pt.)

### Question 4

Use **write.csv()** to save the USA car data to a file. Read it in and check to see that all the factors are correctly set as factors. (10 pt.)

```{r}

```
