---
title: "GEOG-533 Lab 7"
author: Firstname Lastname
output: 
  html_notebook:
    toc: TRUE
    toc_float: TRUE
---

Complete the following exercises in Chapter 8 (Introduction to Regression Analysis) of the textbook [R] pages 247-250. 

## Question 1

This is Exercise 1 in Chapter 8 of the Textbook [R]. (15 pt.)

A regression of weekly shopping trip frequency on annual income (data entered in thousands of dollars) is performed on data collected from 24 respondents. The results are summarized below:

* Intercept: 0.46
* Slope: 0.19

|          | Sum of squares  | Degrees of freedom |  Mean square   |       *F*       |
|----------|-----------------|--------------------|----------------|-----------------|
|Regression|                 |                    |                |                 |
| Residual |       1.7       |                    |                |                 |
| Total    |       2.3       |                    |                |                 |


### Question 1(a)
Fill in the blanks in the ANOVA table.

```{r}

```


|          | Sum of squares  | Degrees of freedom |  Mean square   |       *F*       |
|----------|-----------------|--------------------|----------------|-----------------|
|Regression|                 |                    |                |                 |
| Residual |       1.7       |                    |                |                 |
| Total    |       2.3       |                    |                |                 |


### Question 1(b)
What is the predicted number of weekly shopping trips for someone making $50,000/year?
```{r}

```


### Question 1(c)
In words, what is the meaning of the coefficient 0.19?



### Question 1(d)
Is the regression coefficient significantly different from zero? How do you know?
```{r}

```



### Question 1(e)
What is the value of the correlation coefficient?
```{r}

```





## Question 2

This is Exercise 6 in Chapter 8 of the Textbook [R]. (15 pt.)

The following data are collected in an effort to determine whether snowfall is dependent upon elevation: 

| Snowfall (inches) | Elevation (feet) |
|-------------------|------------------|
|       36          |       400        |
|       78          |       800        |
|       11          |       200        |
|       45          |       675        |

Using R, show your work on exercises (a) through (g).

### Question 2(a)
Find the regression coefficients (the intercept and the slope coefficient).
```{r}

```


### Question 2(b)
Estimate the standard error of the residuals about the regression line.
```{r}

```


### Question 2(c)
Test the hypothesis that the regression coefficient associated with the independent variables is equal to zero. Also place a 95% confidence interval on the regression coefficient.
```{r}

```


### Question 2(d)
Find the value of $r^2$.
```{r}

```


### Question 2(e)
Make a table of the observed values, predicted values, and the residuals.
```{r}

```


### Question 2(f)
Prepare an analysis of variance table portraying the regression results.
```{r}

```


|          | Sum of squares  | Degrees of freedom |  Mean square   |       *F*       |
|----------|-----------------|--------------------|----------------|-----------------|
|Regression|                 |                    |                |                 |
| Residual |                 |                    |                |                 |
| Total    |                 |                    |                |                 |

### Question 2(g)
Graph the data and the regression line.
```{r}

```




## Question 3

This is Exercise 10 in Chapter 8 of the Textbook [R]. (10 pt.)

Use R and the [Milwaukee dataset](http://spatial.binghamton.edu/geog533/data/Milwaukee_Sales.csv) to:

### Problem
perform a regression using sales price as the dependent variable and lot size as the independent variable.

### Solution
```{r}

```



## Question 4

This is Exercise 11 in Chapter 8 of the Textbook [R]. (10 pt.)

Use R and the Hypothetical [UK Housing Prices dataset](http://spatial.binghamton.edu/geog533/data/UK_Housing.csv) to:

### Question 4(a) 
perform a regression using house price as the dependent variable, and number of bedrooms as the independent variable;

```{r}

```


### Question 4(b) 
repeat part (a), using the number of bathrooms as the independent variable, and comment on the results.
```{r}

```



