---
title: "GEOG-533 Lab 9"
author: Firstname Lastname
output: 
  html_notebook:
    toc: TRUE
    toc_float: TRUE
---

## Question 1
Use R package **UScensus2010county** to complete the following tasks:  (20 pt.)

### Question 1(a)
Plot a map of New York counties using the **plot** function.
```{r}

```

### Question 1(b)	
Plot a map of New York counties using the **qtm** function.
```{r}

```


### Question 1(c)	
How many counties in New York State?
```{r}

```

### Question 1(d)	
What’s the 3-digit **fips** code of Broome County?
```{r}

```

### Question 1(e)	
Compute descriptive statistics of the population column (**P0010001**), including total, minimum, maximum, mean, median, and skewness. 
```{r}

```

### Question 1(f)	
Create a histogram and a boxplot of the population.
```{r}

```


## Question 2
Use R package **UScensus2010tract** to complete the following tasks:    (20 pt.)
```{r}

```

### Question 2(a)	
Plot a map of New York census tracts using the **plot** function.
```{r}

```

### Question 2(b)
Compute the total population based on census tracts.
```{r}

```

### Question 2(c)
Select all census tracts in Broome County and plot the map. 
```{r}

```

### Question 2(d)
What’s the total population of Broome County?
```{r}

```

### Question 2(e)
Create a histogram and a boxplot of population based on census tracts of Broome County.
```{r}

```

### Question 2(f)
Select the first five columns of the shapefile of Broome County census tract; add a new population ratio column (= census tract population / county population); save the new shapefile to the hard drive. 
```{r}

```


## Question 3

Use R packages **raster** and **ncdf4** to complete the following tasks:     (20 pt.)
```{r}

```

### Question 3(a)		
Load the multi-band raster dataset “NDVI.nc” into R.
```{r}

```

### Question 3(b)		
Get the basic information about the dataset, including the number of rows, columns, cells, and bands; spatial resolution, extent, bounding box, and projection.
```{r}

```

### Question 3(c)	
Aggregate all bands to generate a mean NDVI raster and a maximum NDVI raster; save the two new raster datasets to the hard drive. 
```{r}

```

### Question 3(d)			
Plot the maps of monthly NDVI of the year 2001
```{r}

```

### Question 3(e)	
Create histograms of monthly NDVI of the year 2001.
```{r}

```

### Question 3(f)			
Plot the NDVI map of July 2000; click any location with data on the map and retrieve the NDVI time series for all years; plot the NDVI time series of the selected location. 
```{r}

```

